Quality Definitions of Qualities

### 2019-12-04 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
updated visibility
updated productivity

@@

\begin{defn}
  A quality of the software production process, referring to its efficiency and
  performance \citep{ghezzi1991fundamentals}.
\end{defn}

\begin{defn}
  The best definition of the productivity of a process is
  \[\text{Productivity} = \dfrac{\text{Outputs produced by the
        process}}{\text{Inputs consumed by the process}}\] Defining inputs. For
  the software process, providing a meaningful definition of inputs is a
  nontrivial but generally workable problem. Inputs to the software process
  generally comprise labor, computers, supplies, and other support facilities
  and equipment. Defining outputs. The big problem in defining software
  productivity is defining outputs. Here we find a defining delivered source
  instructions (DSI) or lines of code as the output of the software process is
  totally inadequate, and they argue that there are a number of deficiencies in
  using DSI. However, most organizations doing practical productivity
  measurement still use DSI as their primary metric \citep{Boehm1987}. \wss{Is
    this a direct quote from \citet{Boehm1987}?  The sentences seem incomplete?}
\end{defn}

\begin{defn}
  \label{ProductivitySelected}
  Productivity is the amount of output (what is produced) per unit of input
  used. If we can measure the size of the software product and the effort
  required to develop the product, we have:
  \begin{align}
    \text{productivity} = \text{size}/\text{effort}
  \end{align}
  Equation (1) assumes that size is the output of the software production
  process and effort is the input to the process. This can be contrasted with
  the viewpoint of software cost models where we use size as an independent
  variable (i.e., an input) to predict effort which is treated as an
  output. Equation (1) is simple to operationalize if we have a single dominant
  size measure, for example, product size measured in lines of code
  \citep{Kitchenham2004}.
\end{defn}

@@

The first sentence of Definition \ref{ProductivitySelected}: Productivity is the
amount of output (what is produced) per unit of input used.

@@

It is concise and measurable. \wss{What is the output?  What is the input?  I
  think the definition needs to give more information on these.  In particular,
  the above definitions focus on code as the output, but documentation, test
  cases etc should also be part of the output.  If we are going to measure this,
  we need a better idea of what we are measuring for outputs and inputs.}

>>>>

\begin{defn}
The degree to which something is seen by the public
\citep{CambridgeVisibility2019}.

The degree to which something is seen or known about
\citep{CambridgeVisibility2019}.
\end{defn}

@@

\begin{defn}
	A quality of the software production process, referring to its efficiency and
	performance \citep{ghezzi1991fundamentals}.
\end{defn}
\begin{defn}
	The best definition of the productivity of a process is
	\[\text{Productivity} = \dfrac{\text{Outputs produced by the
			process}}{\text{Inputs consumed by the process}}\]

Thus, we can improve the productivity of the software process by increasing its
outputs, decreasing its inputs, or both. However, this means that we need to
provide meaningful definitions of the inputs and outputs of the software
process.

\textbf{Defining inputs.} For the software process, providing a meaningful
definition of inputs is a nontrivial but generally workable problem. Inputs to
the software process generally comprise labor, computers, supplies, and other
support facilities and equipment. However, one has to be careful which of
various classes of items are to be counted as inputs. For example:
\begin{itemize}
\item Phases (just software development, or should we include system
engineering, soft-ware requirements analysis, installation, or post development
support?)
\item Activities (to include documentation, project management, facilities
management, conversion, training, database administration?)
\item Personnel (to include secretaries, computer operators, business managers,
contract administrators, line management?)
\item Resources (to include facilities, equipment, communications, current
versus future dollar payments?)
\end{itemize}
An organization can usually reach an agreement on which of the above are
meaningful as inputs in their organizational context. Frequently, one can use
present-value dollars as a uniform scale for various classes of resources.

\textbf{Defining outputs.} The big problem in defining software productivity is
defining outputs. Here we find a defining delivered source instructions (DSI) or
lines of code as the output of the software process is totally inadequate, and
they argue that there are a number of deficiencies in using DSI. However,
	most organizations doing practical productivity measurement still use DSI as
	their primary metric \citep{Boehm1987}. \wss{Is this a direct quote from
		\citet{Boehm1987}?  The sentences seem incomplete?}
\ad{I added some deleted parts, now it is a direct quote. After the ending of
the quote, the following 2 pages discuss the flaws of DCI and a list of
alternatives to DCI, so I ended the quote here.}
\end{defn}
\begin{defn}
	\label{ProductivitySelected1}
Productivity is the amount of output (what is produced) per unit of input used.
In general, productivity is difficult to measure because outputs and inputs are
typically quite diverse and are often themselves difficult to measure. In the
context of software, productivity measurement is usually based on a simple ratio
of product size to project effort. Thus,If we can measure the size of the
software product and the effort required to develop the product, we have:
	\begin{align}
	\text{productivity} = \text{size}/\text{effort}
	\end{align}
Equation (1) assumes that size is the output of the software production process
and effort is the input to the process. This can be contrasted with the
	viewpoint of software cost models where we use size as an independent variable
	(i.e., an input) to predict effort which is treated as an output. Equation (1)
	is simple to operationalize if we have a single dominant size measure, for
	example, product size measured in lines of code \citep{Kitchenham2004}.
\end{defn}
\begin{defn}
	\label{ProductivitySelected2}
The number of lines of new code developed per person-day (an imperfect measure
of productivity but one that could be measured consistently)
\citep{MacCormack2003}.
\end{defn}

@@

The revision of the combination of Definition \ref{ProductivitySelected1} and
Definition \ref{ProductivitySelected2}: Productivity is the
amount of output per unit of input used, which can be measured by the summation
of all output (such as the number of lines of new code, the number of pages of
new documents and the number of new test cases) produced per person-day.

@@

It is concise and measurable. \wss{What is the output?  What is the input?  I
	think the definition needs to give more information on these.  In particular,
	the above definitions focus on code as the output, but documentation, test
	cases etc should also be part of the output.  If we are going to measure this,
	we need a better idea of what we are measuring for outputs and inputs.}
	\ad{I added another def and made it more measurable}
